---
title: "Reproducible Research: Peer Assessment 1"
output: 
html_document:
keep_md: true"
author: "lsaa"
---

This is my first peer assessment on Reproducible Research about personal movement using activity monitoring devices such as a Fitbit, Nike Fuelband, or Jawbone Up. 

## Loading and preprocessing the data
```{r, echo=TRUE}
setwd("C:/Users/Danielle Taneyo/Desktop/Rwork/DataAN")
df <- read.csv("activity.csv")
df$date <- as.Date(df$date)
library(lattice)
library(dplyr)
library(plyr)

```

## What is mean total number of steps taken per day?
```{r, echo=TRUE}
total_step <- tapply(df$steps, df$date, sum, na.rm = TRUE)
mean(total_step)
median(total_step)
histogram(total_step, main = "Total number of steps taken each day", xlab = "")
```

## What is the average daily activity pattern?
```{r, echo=TRUE}
intervalData <- ddply(df, .(interval), summarize, meanInter = mean(steps, na.rm =TRUE))
xyplot(intervalData$meanInter ~ intervalData$interval, type = "l")
intervalData[which.max(intervalData$meanInter),]
```

## Imputing missing values
```{r, echo=TRUE}
sum(is.na(df))
dff <- filter(df, !is.na(steps))
total_dff <- tapply(dff$steps, dff$date, sum)
histogram(total_dff, main = "Total number of steps taken each day", xlab = "")
mean(total_dff)
median(total_dff)
```

## Are there differences in activity patterns between weekdays and weekends?
```{r, echo=TRUE}
dff_week <- mutate(dff, wD = weekdays(date))
```